Parsing Postfix log files

### 2009-03-14 doc/logparser-implementation.tex
Removed all mention of postfix_action, rewriting as necessary.

XXX REWRITE THIS PARAGRAPH\@; FIGURE OUT WHAT THE HELL IS HAPPENING WITH
POSTFIX\_ACTION\@.

Every log line will have a row in the results table, unless the \newline{}
\texttt{postfix\_action} field of the rule which parsed it was INFO or
IGNORE\@.  Each row in the results table is associated with a single
connection; a single connection will have at least one result associated
with it, but will usually have several more, and may have hundreds.

@@

    \textbf{Field}      & \textbf{Value}                                    \\
    name                & Unknown sender domain                             \\
    description         & We do not accept mail from unknown domains        \\
    restriction\_name   & reject\_unknown\_sender\_domain                   \\
    postfix\_action     & REJECTED                                          \\
    program             & \daemon{smtpd}                                    \\
    regex               & \verb!^__RESTRICTION_START__ <(__SENDER__)>: !    \\
                        & \verb!Sender address rejected: Domain not found;! \\
                        & \verb!from=<\k<sender>> to=<(__RECIPIENT__)> !    \\
                        & \verb!proto=E?SMTP helo=<(__HELO__)>$!            \\
    result\_data        &                                                   \\
    connection\_data    &                                                   \\
    action              & DELIVERY\_REJECTED                                \\
    hits                & 0                                                 \\
    hits\_total         & 0                                                 \\
    priority            & 0                                                 \\
    %cluster\_group      & 400                                               \\

@@

    \item [name, description, restriction\_name, and postfix\_action:] are
        not \newline{} used by the parser, they serve to document the rule
        for the user's benefit.

@@

    \item XXX IS THIS CORRECT NOW\@?\newline{}  Are there two or more
        \daemon{smtpd} log lines?  Does the second result have a
        postfix\_action attribute of ACCEPTED\@?  The first two
        \daemon{smtpd} log lines will be a connection log line and a mail
        acceptance log line (Postfix logs acceptance as soon as the first
        recipient has been accepted).

@@

    \item If there are third and subsequent results, are all their
        postfix\_action attributes equal to INFO\@?  If there are any log
        lines after the first two they should be informational only.

@@

    \item Every Postfix process uses a watchdog which kills the process if
        it is not reset for a considerable period of time (five hours by
        default).  This safeguard prevents Postfix processes from running
        indefinitely and consuming resources if a failure causes them to
        enter a stuck state.  XXX IMPROVE THIS SOMEHOW\@.

>>>>

Every recognised log line will have a row in the results table, associated
with a single connection; a single connection will have at least one result
associated with it, but will usually have several more, and may have
hundreds.

@@

    \textbf{Field}      & \textbf{Value}                                    \\
    name                & Unknown sender domain                             \\
    description         & We do not accept mail from unknown domains        \\
    restriction\_name   & reject\_unknown\_sender\_domain                   \\
    program             & \daemon{smtpd}                                    \\
    regex               & \verb!^__RESTRICTION_START__ <(__SENDER__)>: !    \\
                        & \verb!Sender address rejected: Domain not found;! \\
                        & \verb!from=<\k<sender>> to=<(__RECIPIENT__)> !    \\
                        & \verb!proto=E?SMTP helo=<(__HELO__)>$!            \\
    result\_data        &                                                   \\
    connection\_data    &                                                   \\
    action              & DELIVERY\_REJECTED                                \\
    hits                & 0                                                 \\
    hits\_total         & 0                                                 \\
    priority            & 0                                                 \\
    %cluster\_group      & 400                                               \\

@@

    \item [name, description, and restriction\_name:] are not used by the
        parser, they serve to document the rule for the user's benefit.

@@

    \item Was the second result processed by the \texttt{CLONE} action?
        The first two \daemon{smtpd} log lines will be a connection log
        line and a mail acceptance log line; Postfix logs acceptance as
        soon as the first recipient has been accepted.

@@

    \item If there are third and subsequent results, were those log lines
        processed by the \texttt{SAVE\_DATA} action?  If there are any log
        lines after the first two they should be informational only.

@@

    \item Every Postfix process uses a watchdog which kills the process if
        it is not reset for a considerable period of time (five hours by
        default).  This safeguard prevents Postfix processes from running
        indefinitely and consuming resources if a failure causes them to
        enter a stuck state.
